---
title: "October 10, 2020"
author: "Brewpubs and Taprooms in NE Albuquerque"
#date: "10/10/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
```


```{r brewpub-map, echo=FALSE}
#free and apparently unlimited lat/long finder:
#https://www.latlongfinder.net/
beerIcon <- makeIcon(
iconUrl = "http://www.brewingwithbriess.com/Recipes/Assets/Images/beer-images/lager-beer-glass-dark.png", iconWidth = 15*215/230, iconHeight = 31,
iconAnchorX = 31*215/230/2, iconAnchorY = 16
)
beerSites <- c(
  "<a href='https://www.boesebrothersbrewery.com/'>Boese Brothers</a>",
  "<a href='https://quartercelticbrewpub.com/'>Quarter Celtic</a>",
  "<a href='https://www.blacksnoutbrewhouse.com/'>Black Snout Brewpub</a>",
  "<a href='https://www.boxingbearbrewing.com/locations/'>Bridges on Tramway Taproom</a>",
  "<a href='https://www.facebook.com/enchantedcirclebrewing505/'>Enchanted Circle Brewing</a>",
  "<a href='https://draftykiltbrewingco.com/'>Kilt Check</a>",
  "<a href='https://www.lacumbrebrewing.com/'>La Cumbre Brewing</a>",
  "<a href='https://www.canterobrewing.com/'>Cantero Brewing Company</a>",
  "<a href='https://nexusbrewery.com/'>Nexus Brewery</a>",
  "<a href='http://canteenbrewhouse.com/'>Canteen Brewhouse</a>",
  "<a href='https://marblebrewery.com/taprooms/ne-heights'>Marble Brewery</a>",
  "<a href='https://santafebrewing.com/taproom/tin-can-alley/'>Santa Fe Brewing Company</a>",
  "<a href='https://www.starrbrothersbrewing.com/'>Starr Brothers Brewing</a>",
  "<a href='https://brokentrailspirits.com'>Broken Trail Distillery and Brewery</a>",
  "<a href='https://www.b2babq.com/gardenbrewery'>B2B Garden Brewery</a>",
  "<a href='http://canteenbrewhouse.com'>Canteen Brewhouse</a>"
  
  
  
)
brewpubsLatLong <- data.frame(
lat = c(35.1735584, 35.1039452, 35.1081185,35.1162754,35.151175,35.1364451,35.1178573,35.1189447,35.1337231,35.0735494,35.1307415,35.1841663,35.159197,35.1086916,35.122838,35.12051599999999), lng = c(-106.4970957, -106.5148269, -106.5127751,-106.4984764,-106.587741,-106.5894774,-106.6141642,-106.6225612,-106.6065203,-106.4970445,-106.5222683,-106.5759739,-106.5806898,-106.5675915,-106.5519623,-106.6178481))

brewpubsLatLong %>%
leaflet() %>%
addTiles() %>%
addMarkers(icon = beerIcon,popup = beerSites)

```
This is a map of brewpub and taproom locations in Albuquerque, NM (NE Heights only). ABQ is divided into 4 quadrants by two highways; I-25 runs North and South and I-40 runs East and West. I-40 is part of the original Route 66 that began in Chicago, IL and ended in Los Angeles, CA.

Today there are many more brewpubs in Albuquerque than are listed here. So many in fact, that Albuquerque now rivals other craft "beercation" destinations such as Portland, OR, Denver, CO, and Seattle, WA.
