---
title: "Basketball Stats for Kobe Bryant"
subtitle: "2005-2014"
date: "10/17/2020"
output: 
  ioslides_presentation:
    logo: basketballplayer.png
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(magrittr)
library(shiny)
library(tidyverse)
library(ggplot2)
library(plotly)
```

## Overview and Data Description
This Shiny app allows users to explore a few common stats for American basketball player, Kobe Bryant. These stats include:

- Kobe's salary each year
- The number of games Kobe played each year
- The number of minutes Kobe played each year
- The number of points Kobe scored each year

Although Kobe's playing career spanned 20 years from 1996-2016, the stats here only cover 2005-2014.

## How to use the Shiny App

- Select a statistic from the drop down box to view a line chart of values for that statistic over the time period.    

- The default value of the line chart is 'Salary' with the line graph showing how much Kobe earned each year.  

- Select a different statistic to view corresponding values over time.  

- **To advance to the next slide, click to the right of the slide on the black border**

## Kobe Bryant's Stats (2005-2014)

```{r player-comparison, echo = FALSE}
player_data <- read.csv("playerstats_kobe.csv",colClasses=c("numeric","numeric","numeric","numeric"))

ui <- fluidPage(
  fluidRow(
    column(4,
            selectInput("selected_parameter",
              "Select Statistic",    
              choices=c("Salary","Games","Minutes","Points")
            )
          )
  ),
  fluidRow(
    column(8,plotOutput("annual_plot"))
  )
)
server <- function(input,output,session) {
  annual_results <- reactive({
    years.df <- data.frame(year=c(2005:2014))
    pd <- player_data[,input$selected_parameter]
    ar <- cbind(years.df,pd)
  })
  output$annual_plot <- renderPlot({
    ggplot(annual_results(), aes(x=year,y=pd)) +
      geom_line() +
      scale_y_continuous(labels = scales::label_comma()) +
      scale_x_continuous(breaks = 2005:2014) + 
      labs(x= "Years",y="")
  })
}
shinyApp(ui,server,session)
```

## Links and Thanks

[Kobe Bryant Basketball Statistics](https://www.basketball-reference.com/players/b/bryanko01.html)  

[Kobe Bryant Biography - Wikipedia](https://en.wikipedia.org/wiki/Kobe_Bryant)


