---
title: "Basketball Stats for Famous Players"
subtitle: "2005-2014"
date: "10/17/2020"
runtime: shiny
output: 
  ioslides_presentation:
    logo: basketballplayer.png
  slidy_presentation: default
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(magrittr)
library(shiny)
library(ggplot2)
library(plotly)
library(DT)
```

## Basketball Player Comparisons
This Shiny app allows the user to compare 10 famous American basketball players between the years of 2005-2014. These 10 players include:   

[add players here]

```{r echo=FALSE,results='asis'}
#library(knitr)
#library(kable)
#knitr::kable(Players.df[,2:3],col.names=c("",""))
```

Players can be compared on the basis of Salary, Games played, Minutes played, and Points scored. 

## How to use the Shiny App

To compare players, select a comparison parameter from the drop down box. The line chart will automatically update that parameter for each player for each year. 

## Kobe Bryant's Stats (2005-2014)

```{r player-comparison, echo = FALSE}
#seasons <- c("2005","2006","2007","2008","2009","2010","2011","2012","2013","2014")
player_data <- read.csv("playerstats_kobe.csv",colClasses=c("numeric","numeric","numeric","numeric"))

ui <- fluidPage(
  #titlePanel("Basketball Player Comparison"),
  fluidRow(
    column(4,selectInput("selected_parameter","Parameter", choices=c("Salary","Games","Minutes","Points")))
  ),
  fluidRow(
    column(8,plotOutput("annual_plot"))
  )
)

server <- function(input,output,session) {
  annual_results <- reactive({
    years.df <- data.frame(year=c(2005:2014))
    pd <- player_data[,input$selected_parameter]
    ar <- cbind(years.df,pd)
    print(ar)
  })
  
  output$annual_plot <- renderPlot({
    ggplot(annual_results(), aes(x=year,y=pd)) +
      geom_line() +
      labs(x= "Years",y="")
  })
}
shinyApp(ui,server,session)
```

## Links and Thanks

```{r pressure}
plot(pressure)
```
